Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-06-26 doc/PRF2022/PRF_main.tex
Peter working on manuscript

\begin{figure}
  \begin{center}
      \includegraphics[width=0.22\textwidth]{VS_0.pdf}
      \includegraphics[width=0.22\textwidth]{VS_1.pdf}
   \includegraphics[width=0.22\textwidth]{VS_2.pdf}
   \includegraphics[width=0.22\textwidth]{VS_3.pdf}\\
         \includegraphics[width=0.22\textwidth]{BS_0.pdf}
      \includegraphics[width=0.22\textwidth]{BS_1.pdf}
   \includegraphics[width=0.22\textwidth]{BS_2.pdf}
   \includegraphics[width=0.22\textwidth]{BS_3.pdf}
%   Panels (e)-(f) same but for non-vesicle initial configuration
  \end{center}
  \caption{
    \label{fig:BC1_shear_flow}
    The figure shows a vesicle in shear flow (panels (a)-(d), $\dot \gamma = ...$) 
    and the multiple component bilayers in shear (panels (e)-(f), $\dot \gamma = ...$).}
\end{figure}

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{VTG_E.pdf}
   \includegraphics[width=0.3\textwidth]{VTG_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{VTG_MSD.pdf}\\
  \includegraphics[width=0.3\textwidth]{BTG_E.pdf}
   \includegraphics[width=0.3\textwidth]{BTG_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{BTG_MSD.pdf}
  \end{center}
\caption{A vesicle in Taylor-Green flows when the flow strength $V_0=\{0.1, 0.15, 0.2\}$. }
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.22\textwidth]{VTG_0.pdf}
  \includegraphics[width=0.22\textwidth]{VTG_1.pdf}
  \includegraphics[width=0.22\textwidth]{VTG_2.pdf} 
    \includegraphics[width=0.22\textwidth]{VTG_3.pdf} \\
      \includegraphics[width=0.22\textwidth]{BTG_0.pdf}
  \includegraphics[width=0.22\textwidth]{BTG_1.pdf}
  \includegraphics[width=0.22\textwidth]{BTG_2.pdf} 
    \includegraphics[width=0.22\textwidth]{BTG_3.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BTG_flow} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.4\textwidth]{VTG_Area}
  \includegraphics[width=0.4\textwidth]{VTG_Len}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:VTG_AreaLen} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
\end{figure}

@@

%
%\begin{figure}
%  \begin{center}
%  \includegraphics[width=0.32\textwidth]{shear_0.png}
%  \includegraphics[width=0.32\textwidth]{shear_1000.png}
%  \includegraphics[width=0.32\textwidth]{shear_2000.png} 
%  \end{center}
%  \vspace{-20pt}  
%  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
%\end{figure}
%
%\begin{figure}
%  \begin{center}
%  \includegraphics[width=0.32\textwidth]{TG_0.png}
%  \includegraphics[width=0.32\textwidth]{TG_2500.png}
%  \includegraphics[width=0.32\textwidth]{TG_5000.png}
%  \end{center}
%  \vspace{-20pt}  
%  \caption{\label{fig:TG_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(b) in a Taylor-Green flow when $V_0=0.1$ and $l=0.5$.}
%\end{figure}
\subsection{Boundary condition (ii):  multilamellar configurations}

@@

%\begin{figure}
%  \begin{center}
%  \includegraphics[width=0.21\textwidth]{shear_checker_0.png}
%  \includegraphics[width=0.21\textwidth]{shear_checker_250.png}
%  \includegraphics[width=0.21\textwidth]{shear_checker_500.png}
%  \includegraphics[width=0.21\textwidth]{shear_checker_750.png} \\
%%  \includegraphics[width=0.4\textwidth]{lambda_fig1.jpg}
%  \end{center}
%  \vspace{-20pt}  
%  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
%\end{figure}
%
\subsection{Boundary condition (iii): striated configurations}

>>>>

\begin{figure}
  \begin{center}
      \includegraphics[width=0.22\textwidth]{VS_0.pdf}
      \includegraphics[width=0.22\textwidth]{VS_1.pdf}
   \includegraphics[width=0.22\textwidth]{VS_2.pdf}
   \includegraphics[width=0.22\textwidth]{VS_3.pdf}\\
         \includegraphics[width=0.22\textwidth]{BS_0.pdf}
      \includegraphics[width=0.22\textwidth]{BS_1.pdf}
   \includegraphics[width=0.22\textwidth]{BS_2.pdf}
   \includegraphics[width=0.22\textwidth]{BS_3.pdf}
%   Panels (e)-(f) same but for non-vesicle initial configuration
  \end{center}
  \caption{
    \label{fig:BC1_shear_flow}
    The figure shows a vesicle in shear flow (panel (a) shows the pre-relaxed initial configuration; panels (b)-(d): $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=160$) 
    and the multiple component bilayers in shear flow (The insets of Fig~\ref{fig:relax}b is used for panels (e); panels (f)-(h): $\dot \gamma = \{0.05, 0.075, 0.1\}$ at $t=600$). The streamlines are plotted in the background. }
\end{figure}

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{VTG_E.pdf}
   \includegraphics[width=0.3\textwidth]{VTG_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{VTG_MSD.pdf}\\
  \includegraphics[width=0.3\textwidth]{BTG_E.pdf}
   \includegraphics[width=0.3\textwidth]{BTG_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{BTG_MSD.pdf}
  \end{center}
\caption{A vesicle in Taylor-Green flows when the flow strength $V_0=\{0.1, 0.15, 0.2\}$. The result indicates that the highest flow strength ($V_0=0.2$) makes the vesicle (top row) rupture within a short period of time and the energy rapidly increases. As expected, the local order parameter drops and the MSD increases. For bilayer structure (bottom row), for $V_0=0.15$ and $V_0 = 0.2$, the energy gradually increases over the time but the other two measures do not have  a clear trend.}
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.22\textwidth]{VTG_0.pdf}
  \includegraphics[width=0.22\textwidth]{VTG_1.pdf}
  \includegraphics[width=0.22\textwidth]{VTG_2.pdf} 
    \includegraphics[width=0.22\textwidth]{VTG_3.pdf} \\
      \includegraphics[width=0.22\textwidth]{BTG_0.pdf}
  \includegraphics[width=0.22\textwidth]{BTG_1.pdf}
  \includegraphics[width=0.22\textwidth]{BTG_2.pdf} 
    \includegraphics[width=0.22\textwidth]{BTG_3.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BTG_flow} The figure shows a vesicle in Taylor-Green flow (panel (a) shows the pre-relaxed initial configuration; panels (b)-(d): $V_0 = \{0.1, 0.15, 0.2\}$ at $t=600$) 
    and the multiple component bilayers in Taylor-Green flow (The insets of Fig~\ref{fig:relax}b is used for panels (e); panels (f)-(h): $V_0 = \{0.1, 0.15, 0.2\}$ at $t=200$). The streamlines are plotted in the background.
  }
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.4\textwidth]{VTG_Area}
  \includegraphics[width=0.4\textwidth]{VTG_Len}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:VTG_AreaLen} Vesicle in a Taylor-Green flow where $V_0=0.1$ and the size of rotating cell $l$ is varied. The enclosed area calculated from the bilayer midplane decreases over time and the total length measured from the midplane remains nearly constant with small magnitude of oscillations. }
\end{figure}

@@

\subsection{Boundary condition (ii):  multilamellar configurations}

@@

\subsection{Boundary condition (iii): striated configurations}
